Reading Notes

### 2020-09-14 1summ.tex
incorporating edits and final pass

Already the effects of human-influenced climate change are readily apparent and devastating. %%<hurtng everyone in particular poor and disadvantaged groups>.
Burning fossil fuels for energy is the main contributor to rising $CO_{2}$ levels, and the energy demand is only increasing.
This increase in energy demand along with the need to protect our climate makes finding efficient, renewable energy technologies of the utmost importance.
Harvesting the abundant solar energy is a good solution because it is renewable, non-polluting, sustainable.
Devices which convert light to electricity, called photovoltaics, were originally made of silicon and required rare elements and careful, clean-room processing.
More recently, organic photovoltaic (OPV) devices have recieved attention for their simple, inexpensive manufacture.
Generally OPV devices are made of a multicompound mixture: usually an electron donor and acceptor which form a mosaic-like structure called a bulk-heterojunction (BHJ).
The compounds and polymers used in OPVs are made of common elements and can be synthesized with relative ease.
And the OPV BHJ can often be assembled using simple techniques like roll to roll printing in ambient conditions.
The process for OPV to generate electricity is as follows: 
Sunlight excites an electron, which forms an exciton.
This exciton travels to an acceptor/donor interface and is dissociated into free electron and hole.
Then the free charges travel to an electrode which generates current.
However, in order for OPV devices to be a viable solution, they need to be more efficient.
The efficiency of an OPV device can be improved by changing the chemistry of the electron acceptor and donor compounds, the polymer properties, and tuning the processing conditions of the BHJ.
With so many parameters, quickly this becomes an intractable problem for experiments to solve.
This is where molecular simulation comes in.

@@

Coarse grain (CG) models, which group multiple atoms together into "super atoms" and using an effective potential to specify the forces acting upon the site, can be used to access length and time scales more relevant to the bulk polymer morphology.
After a bulk morphology is obtained, we can use backmapping, a process in which the atomistic detail can be reintegrated into a coarse grain model, to restore atomistic detail for use in simulations like KMC/QCC.
This multiscale simulation workflow allows for OPV morphologies to be equilibrated at length scales relevant to the bulk polymer and to regain the atomistic detail more efficiently using a better starting structure.
Currently software packages exist that do this but they require tedious manual input and are highly susceptible to user error.
PI Fothergill will design a simple, chemically sensible coarse graining and backmapping package based on the SMILES chemical input language with a focus on OPVs.
This will allow for easier setup and execution of multiscale simulation, which can be part of the process to finding the next great OPV technology.

@@

The proposed work is original, taking a systems view of software interoperability needed to improve organic photovoltaics with molecular simulation.
Through focus on transferable, reproducible, usable, and extensible simulation infrastructure, the proposed work is positioned to transform both the manufacturing of sustainable power technologies and the norms of practice in computational materials science.
The intellectual merit of project components---coarse-graining pipelines and multiscale simulations---includes the potential to transform materials simulations adjacent to organic photovoltaics, including polymers for structural composites and molecules of biomedical interest.
The specific insight into structure-property relationships in OPV materials also has intellectual transferability to broader polymer assembly problems, and charge transport problems of interest in piezoelectric materials, induction welding of polymers, and organic electronics broadly.
PI Fothergill is positioned to be successful in the propsed work, with published expertise in quantum chemical methods applied to charge transport in organic dyes, organometallic crystals, and coarse-grained materials simulation; and as a trained Software Carpentry instructor, and open-source project contributor.
Ample computational resources are available to complete the proposed work, in the form of local HPC resources (Fry: 32 NVIDIA Pascal P100 gpus, R2: 28 P100 GPUs, Borah: ~30 GPUs coming online this year), Idaho resources (Idaho National Lab facilities: 100's of V100 GPUs) and national resources (125,000 GPU-hour allocation on XSEDE Bridges ).

>>>>

Already the effects of human-influenced climate change are readily apparent and devastating. %%<hurtng everyone in particular poor and disadvantaged groups>.
Burning fossil fuels for energy is the main contributor to rising $CO_{2}$ levels, and the energy demand is only increasing.
This increase in energy demand along with the need to protect our climate makes finding efficient, renewable energy technologies of the utmost importance.
Harvesting the abundant solar energy is a good solution because it is renewable, non-polluting, and sustainable.
Devices which convert light to electricity, called photovoltaics, were originally made of silicon and required rare elements and careful, clean-room processing.
More recently, organic photovoltaic (OPV) devices have recieved attention for their simple, inexpensive manufacture.
Generally OPV devices are made of a multicompound mixture: usually an electron donor and acceptor which form a mosaic-like structure called a bulk-heterojunction (BHJ).
The compounds and polymers used in OPVs are made of common elements and can be synthesized with relative ease.
And the OPV BHJ can often be assembled using simple techniques like roll to roll printing in ambient conditions.
The process for OPV to generate electricity is as follows: 
Sunlight excites an electron, which forms an exciton.
This exciton travels to an acceptor/donor interface and is dissociated into free electron and hole.
Then the free charges travel to an electrode which generates current.
However, in order for OPV devices to be a viable solution, they need to be more efficient.
The efficiency of an OPV device can be improved by changing the chemistry of the electron acceptor and donor compounds, the polymer properties, and tuning the processing conditions of the BHJ.
With so many parameters, quickly this becomes an intractable problem for experiments to solve.
This is where molecular simulation comes in.

@@

Coarse grain (CG) models, which group multiple atoms together into "super atoms" and use an effective potential to specify the forces acting upon the site, can be used to access length and time scales more relevant to the bulk polymer morphology.
After a bulk morphology is obtained, we can use backmapping, a process in which the atomistic detail can be reintegrated into a coarse grain model, to restore atomistic detail for use in simulations like KMC/QCC.
This multiscale simulation workflow allows for OPV morphologies to be equilibrated at length scales relevant to the bulk polymer and to regain the atomistic detail more efficiently using a better starting structure.
Currently software packages exist that do this but they require tedious manual input and are highly susceptible to user error.
PI Fothergill will design a simple, chemically sensible coarse graining and backmapping package based on the SMILES chemical input language with a focus on OPVs.
This will allow for easier setup and execution of multiscale simulation, which can be part of the process to finding the next great OPV technology.

@@

The proposed work is original, taking a systems view of software interoperability needed to improve organic photovoltaics with molecular simulation.
Through focus on transferable, reproducible, usable, and extensible simulation infrastructure, the proposed work is positioned to transform both the manufacturing of sustainable power technologies and the norms of practice in computational materials science.
The intellectual merit of project components---coarse-graining pipelines and multiscale simulations---includes the potential to transform materials simulations adjacent to organic photovoltaics, including polymers for structural composites and molecules of biomedical interest.
The specific insight into structure-property relationships in OPV materials also has intellectual transferability to broader polymer assembly problems, and charge transport problems of interest in piezoelectric materials, induction welding of polymers, and organic electronics broadly.
PI Fothergill is positioned to be successful in the proposed work, as a trained Software Carpentry instructor and open-source project contributor with published expertise in quantum chemical methods applied to charge transport in organic dyes, organometallic crystals, and coarse-grained materials simulation.
Ample computational resources are available to complete the proposed work, in the form of local HPC resources (Fry: 32 NVIDIA Pascal P100 gpus, R2: 28 P100 GPUs, Borah: ~30 GPUs coming online this year), Idaho resources (Idaho National Lab facilities: 100's of V100 GPUs) and national resources (125,000 GPU-hour allocation on XSEDE Bridges ).
